Perihelion advance of Mercury

### 2020-09-25 perihelion_advance_of_mercury.Rmd
replace triple backtics with single

Consider the following R idiom, in which ```trajectory()``` is used to
directly simulate a geodesic in Schwarzschild space:

@@

(NB ```trajectory()``` takes geometrized units).  In the above, we see
a typical trajectory in Schwarzschild space with a precession of
around 40 degrees per orbit.  As a consistency check we can perform
the same calculation but with Newtonian approximations:

@@

We need to isolate the change points, here found isolating iterations
$i$ such that ```r[i-1]<r[i]``` and r[i]>r[i+1]```:

>>>>

Consider the following R idiom, in which `trajectory()` is used to
directly simulate a geodesic in Schwarzschild space:

@@

(NB `trajectory()` takes geometrized units).  In the above, we see
a typical trajectory in Schwarzschild space with a precession of
around 40 degrees per orbit.  As a consistency check we can perform
the same calculation but with Newtonian approximations:

@@

We need to isolate the change points, here found isolating iterations
$i$ such that `r[i-1]<r[i]` and `r[i]>r[i+1]`:
